---
title: "IMtool2"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
---

```{r setup, include=FALSE}
library(ggplot2)
library(plotly)
library(plyr)
library(flexdashboard)

```

Patents
=======================================================================

```{r include=FALSE}
library(patentsview)
library(dplyr)
library(highcharter)
library(DT)
library(knitr)
library(visNetwork)
library(magrittr)
library(stringr)

### Query Function
query <- with_qfuns(
      or(
            text_phrase(patent_abstract = "autonomous vehicles"),
            text_phrase(patent_title = "autonomous vehicles")
      )
)

# Create a list of the fields we'll need for the analysis:
fields <- c("patent_number", "assignee_organization",
            "patent_num_cited_by_us_patents", "app_date", "patent_date",
            "assignee_total_num_patents")

# Send an HTTP request to the PatentsView API to get data:
pv_out <- search_pv(query = query, fields = fields, all_pages = TRUE)
```


Row
-----------------------------------------------------------------------

### Top Assignes


### Citation rate


Row
-----------------------------------------------------------------------

### Citation Network

### Citation Network 2

Scientometric
=======================================================================

```{r include=FALSE}
library(bibliometrix)
library(treemap)
library(tm)
library(pander)
library(knitr)

Dtisi <- readFiles("~/MEGA/IMTOOL2/IMtool2/data/savedrecs.bib")
database <- convert2df(Dtisi, dbsource = "isi", format = "bibtex")
df <- biblioAnalysis(database, sep = ";")
df.summary <- summary(object = df, k = 10, pause = FALSE)
```


Row
-----------------------------------------------------------------------

### Top Articles 

```{r}
knitr::kable(df.summary$MostCitedPapers)
```

### Most Productive Countries

```{r}
knitr::kable(df.summary$TCperCountries, align = 'c')
```

Row
-----------------------------------------------------------------------

### Most Relevant Sources

```{r}
knitr::kable(df.summary$MostRelSources)
```

### Most Related Keyword

```{r}
knitr::kable(df.summary$MostRelKeywords)
```

Trends
=======================================================================

```{r include=FALSE}
library(gtrendsR)
library(forecast)
library(tseries)

keyword = c("autonomous vehicles", "self driving cars")

res = gtrends(keyword, geo = "", time = "all", gprop = "web", category = 0, hl = "en-US")

keyword_pt = "carro autonomo"

res_pt = gtrends(keyword_pt, geo = "BR", time = "all", gprop = "web", category = 0)

gt.fc.en <- res$interest_over_time
fc.en <- forecast(res$hits)

xt_en <- window(gt.fc.en[,2],end=218)
xf_en <- window(gt.fc.en[,2],start=219)

gt.fc.br <- res_pt$interest_over_time
fc.br <- forecast(res_pt$hits)

xt_pt <- window(gt.fc.br[,2],end=100)
xt_pt <- window(gt.fc.br[,2],start = 101)
```


Row
-----------------------------------------------------------------------

### Google Trends World

```{r}
plot(res)
```

### Forecast analysis - EN

```{r}
rwd_en <- rwf(xt_en,drift=T,h=25)
plot(rwd_en,main="Random Walk with Drift Method",ylab="Level",xlab="Tseries")
lines(gt.fc.en[,2])
```

Row
-----------------------------------------------------------------------

### Google Trends - Brasil

```{r}
plot(res_pt)
```

### Forecast Analysis - Brazil

```{r}
rwd_br <- rwf(xt_pt,drift=T,h=66)
plot(rwd_br,main="Random Walk with Drift Method",ylab="Level",xlab="Months")
lines(gt.fc.br[,2])
```

News
=======================================================================

```{r}
library(tm.plugin.webmining)
yahoonews <- WebCorpus(YahooNewsSource("Autonomous vehicles"))
googlenews <- WebCorpus(GoogleNewsSource("Autonomous vehicles"))
```


Row
-----------------------------------------------------------------------

### News Trends

```{r}

```

### Add Conditional Density Curves to Plot

```{r}

```

Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together

```{r}

```

### Density and Scatterplot Overlay Using geom_density

```{r}

```

OECD
=======================================================================

Row
-----------------------------------------------------------------------

### stat_density Example

```{r}

```

### Add Conditional Density Curves to Plot

```{r}

```

Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together

```{r}

```

### Density and Scatterplot Overlay Using geom_density

```{r}

```

EUROSTAT
=======================================================================

Row
-----------------------------------------------------------------------

### stat_density Example

```{r}

```

### Add Conditional Density Curves to Plot

```{r}

```

Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together

```{r}

```

### Density and Scatterplot Overlay Using geom_density

```{r}

```

Trends Series (BETS)
=======================================================================

Row
-----------------------------------------------------------------------

### stat_density Example

```{r}

```

### Add Conditional Density Curves to Plot

```{r}

```

Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together

```{r}

```

### Density and Scatterplot Overlay Using geom_density

```{r}

```

Twitter
=======================================================================

Row
-----------------------------------------------------------------------

### stat_density Example

```{r}

```

### Add Conditional Density Curves to Plot

```{r}

```

Row
-----------------------------------------------------------------------

### geom_density and facet_wrap Together

```{r}

```

### Density and Scatterplot Overlay Using geom_density

```{r}

```
