---
title: "Bibliometric Routine"
author: "Fábio Rocha Campos"
date: "14 de setembro de 2017"
output:
  output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
### Load Packages
library(bibliometrix)
library(treemap)
library(tm)
library(pander)
library(knitr)
```

## Objetivo

Estabelecer um script pronto para análise de bibliometria e cientometria para consultas realizadas no ISI - Web Of Knowledge <http://www.webofknowledge.com/>

Este script é baseado no pacote "Bibliometrix" <http://www.bibliometrix.org/> para R. Na aba Documents é possível baixar um tutorial para preparar os dados para rodar no pacote. 

Sendo assim, o script abaixo considera que o usuário já baixou a consulta em .txt ou .bib. 
A título de demonstração consultamos no ISI o termo "autonomous vehicles" e selecionamos apenas áreas que se refere aos "veículos autonômos" que estão sendo desenvolvidos para o ambiente urbano. 

O documento consta apenas os resultados sendo que o script em formato .RMD ou .R pode ser obtido neste link: <https://github.com/fabiorcampos/Bibliometric-Routines>

### Resumo

```{r, echo=FALSE, results='hide'}
### Load and prepare Data
Dtisi <- readFiles("./data/savedrecs.bib")
database <- convert2df(Dtisi, dbsource = "isi", format = "bibtex")
df <- biblioAnalysis(database, sep = ";")
df.summary <- summary(object = df, k = 10, pause = FALSE)
```

**Main Information**

```{r, echo=FALSE, comment=NA, message=F, warning=F}
df.summary$MainInformation
```


**Annual Scientific Production**

```{r echo=FALSE}
Y = table(df$Years)
  Ym = table(df$Years[df$nAUperPaper>1])
  plot(as.numeric(row.names(Y)),Y,type="l",main="Articles per Year",xlab="Year",ylab="Number of Articles",col="blue")
  lines(as.numeric(row.names(Ym)),Ym,col="red")
legend(x="topleft",c("Total Articles","Multi Auth. Articles"),col=c("blue","red"),lty = c(1, 1),cex=0.8,bty="n")

  TCY=aggregate(df$TotalCitation,list(df$Years),"sum")
  plot(as.numeric(row.names(Y)),TCY[,2]/Y,type="l",main="Average Citations per Article",xlab="Year",ylab="Average Citations",col="blue")
  lines(as.numeric(row.names(Y)),Y,col="red")
legend(x="topright",c("Average Citations","N. of Articles"),col=c("blue","red"),lty = c(1, 1),cex=0.6,bty="n")
```


**Most Productive Authors**

```{r, echo=FALSE,comment=NA, message=F, warning=F}
knitr::kable(df.summary$MostProdAuthors)
```

**Top Manuscripts**

```{r, echo=FALSE}
knitr::kable(df.summary$MostCitedPapers)
```

**Most Productive Countries**

```{r echo=FALSE}
barplot(sort(df$Countries,decreasing=TRUE)[1:10],horiz=TRUE,las=2,cex.names=0.6,main="Most Productive Countries",xlab="Articles", col = "blue")
```

**Total Citations per Country**

```{r, echo=FALSE}
knitr::kable(df.summary$TCperCountries, align = 'c')
```

**Most Relevant Sources**

```{r, echo=FALSE}
knitr::kable(df.summary$MostRelSources)
```

**Most Related Keywords**

```{r, echo=FALSE}
knitr::kable(df.summary$MostRelKeywords)
```

## Authors' Dominance ranking

The function dominance calculates the authors’ dominance ranking as proposed by Kumar & Kumar, 2008.

```{r, echo=FALSE}
DF <- dominance(df, k = 10)
knitr::kable(DF)
```


## Authors' h-index

The h-index is an author-level metric that attempts to measure both the productivity and citation impact of the publications of a scientist or scholar.

```{r}
authors=gsub(","," ",names(df$Authors)[1:10])

indices <- Hindex(database, authors, sep = ";",years=50)

knitr::kable(indices$H)
```

## Lotka's Law coefficient estimation

Lotka’s law describes the frequency of publication by authors in any given field as an inverse square law, where the number of authors publishing a certain number of articles is a fixed ratio to the number of authors publishing a single article. 

```{r}
L <- lotka(df)
# Author Productivity. Empirical Distribution
knitr::kable(L$AuthorProd)
```

## Bibliometric network matrices


## Bibliographic coupling

```{r}
NetMatrix <- biblioNetwork(database, analysis = "coupling", network = "authors", sep = ";")

# calculate jaccard similarity coefficient
S <- normalizeSimilarity(NetMatrix, type="jaccard")

# plot authors' similarity (first 20 authors)
net=networkPlot(S, n = 10, Title = "Authors' Coupling", type = "fruchterman", size=FALSE,remove.multiple=TRUE)
```

## Bibliographic co-citation